---
title: "Convergence-MCMC"
author: "Chimeddulam Dalaijamts"
date: "Mrch 1, 2021"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    source_code: embed
    storyboard: true
    orientation: columns
---

<style type="text/css">    


body{ /* Normal  */
      font-size: 14px;
  }
td {  /* Table  */
  font-size: 7px;
}
h1.title {
  font-size: 12pt;
  color: Maroon;
}
h1 { /* Header 1 */
  font-size: 12px;
  color: DarkBlue;
}
h2 { /* Header 2 */
  font-size: 28px;
  color: Maroon;
}
h3 { /* Header 3 */
  font-size: 30px;
  color: DarkRed;
}
code.r{ /* Code block */
    font-size: 10px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 12px;
}
</style>



Overview {data-icon="fa-list"}
=====================================

##  Mouse PERC-PBPK modeling for 3 strains + CC 45 strains

### MCMC convergence analysis

* MCMC simulations of 43 parameter combined original + restarted:
    + Original 60k + Restarted 60k (120k)
    + Run on MCSim v.5.6.5 software in Terra cluster in the High Performance Research Center, TAMU


* Convergence analysis:
  + Gelman and Rubin’s convergence diagnostic - using 'coda' R package
  + Trace plot of MCMC output - using 'coda' R package
  + Kernel Density
  + Cross correlation - usin 'corrplot' R package
  + Likelihood of chains



Convergence {data-icon="fa-table"}
=====================================  


Column {data-width=200}
-------------------------------------


### Gelman diagnosis -  original 60k + restarted 60k


```{r Read MCMC 120k, echo= FALSE}
library(coda)
library(reshape2)
library(ggplot2)
library(corrplot)
# Read MCMC chains
x1 = as.mcmc(read.table(file="perc.mouse.48strains.43p.mcmc.1.60.out", header=T)[3001:12001,])
x2 = as.mcmc(read.table(file="perc.mouse.48strains.43p.mcmc.2.60.out", header=T)[3001:12001,])
x3 = as.mcmc(read.table(file="perc.mouse.48strains.43p.mcmc.3.60.out", header=T)[3001:12001,])
x4 = as.mcmc(read.table(file="perc.mouse.48strains.43p.mcmc.4.60.out", header=T)[3001:12001,])
x1m <- x1[,2:44, drop=FALSE]
x2m <- x2[,2:44, drop=FALSE]
x3m <- x3[,2:44, drop=FALSE]
x4m <- x4[,2:44, drop=FALSE]
combinedchains3 = mcmc.list(x1m, x2m, x3m, x4m)

# Read MCMC chains for density
mcmc.chain1 = read.delim("perc.mouse.48strains.43p.mcmc.1.60.out")[5001:12001,]
mcmc.chain2 = read.delim("perc.mouse.48strains.43p.mcmc.2.60.out")[5001:12001,]
mcmc.chain3 = read.delim("perc.mouse.48strains.43p.mcmc.3.60.out")[5001:12001,]
mcmc.chain4 = read.delim("perc.mouse.48strains.43p.mcmc.4.60.out")[5001:12001,]
M.chain1 <- mcmc.chain1[,c(2:44)]
M.chain2 <- mcmc.chain2[,c(2:44)]
M.chain3 <- mcmc.chain3[,c(2:44)]
M.chain4 <- mcmc.chain4[,c(2:44)]
M.chain1$chain <- 1
M.chain2$chain <- 2
M.chain3$chain <- 3
M.chain4$chain <- 4
Combined3 <- rbind(M.chain1, M.chain2, M.chain3, M.chain4)
Param3 <- melt(Combined3, id = "chain")

gelman.diag(combinedchains3)

#Select LnData
LnD.chain1 <- mcmc.chain1[,c(1,2177)]
LnD.chain2 <- mcmc.chain2[,c(1,2177)]
LnD.chain3 <- mcmc.chain3[,c(1,2177)]
LnD.chain4 <- mcmc.chain4[,c(1,2177)]
LnD.chain1$chain <- 1
LnD.chain2$chain <- 2
LnD.chain3$chain <- 3
LnD.chain4$chain <- 4
Combined.LnD.3 <- rbind(LnD.chain1, LnD.chain2, LnD.chain3, LnD.chain4)
lnData3 <- melt(Combined.LnD.3, id = c("chain","iter"))
```


Column {data-width=500}
--------------------------------------------------


### 2 Original 60k + restarted 60k


#### **Traceplot**

```{r traceplot 2, out.width="90%", fig.show='hold', fig.height = 4.2, fig.width = 11, echo = FALSE}
par(mfrow = c(5, 9), mar = c(2, 1.5, 1, 1) + 0.1, oma = c(0, 2, 0, 0), las = 1, #pty = "m",lab = "bottom"
    xaxs = "i", yaxs = "i", cex.axis = 0.9, cex.main = 0.9)
traceplot(combinedchains3,smooth = TRUE)
```



#### **Kernel Density**

```{r density 2, out.width="90%", fig.height = 4.2, fig.width = 11, echo = FALSE}

ggplot(data = Param3, aes(x = value, colour=factor(chain))) + 
  # scale_x_log10() +
  scale_colour_manual(values=c("black", "red", "green", "blue")) + 
  geom_line(stat="density", size=1) + 
  theme(legend.position="none") +
  labs(x = "iterations", y = "Density", title = "") +
  facet_wrap(~variable, scales = "free", ncol = 9, dir="h") +
  theme(strip.background = element_rect(fill="white", colour="white"),
        panel.background = element_rect(fill="white", colour="white"),
        # plot.title = element_text(size=12, face="bold"),
        axis.text = element_text(size=8))
```



Column {data-width=300}
--------------------------------------------------


### Restarted from 50kth


#### Cross correlation


```{r corrplot, echo = FALSE}
Combined3$chain <- NULL
Mean.cor3 <- cor(Combined3)
par(mfrow = c(1, 1))
corrplot.mixed(Mean.cor3, lower="number", upper="color", 
               mar = c(0, 0, 0, 0), tl.cex=0.5, tl.pos = "lt", tl.col="black", number.cex = 0.4)
```


#### Likelihood of chains


```{r plot lnData3, out.width="90%", fig.height=3, fig.width=8, echo = FALSE}
ggplot(data = lnData3, aes(x = value, colour=factor(chain))) + 
  scale_colour_manual(values=c("black","red", "green", "blue")) +
  geom_line(stat="density", size=1.5) + 
  theme(legend.position="bottom") +
  labs(y="density", x="LnData", title = "") +
  # facet_wrap(~variable, scales = "free", nrow = 11, dir="h") + #ncol
  theme(strip.background = element_rect(fill="white", colour="white"),
        axis.text = element_text(size=7), 
        strip.text = element_text(size=8),
        panel.background = element_rect(fill="white", colour="white"))
```


  